---
title: "Week11-twitter"
author: "Jiayin Qu"
date: "3/28/2020"
output: pdf_document
---
# Library Imports
```{r twiter api setup, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(twitteR)
library(stringr)
api <- 'e0y2pHHrYtT320wP8WSsPa0i7'
apiSecret <- 'Ewv63M79SR6ocpWGbW5lpOgiX3z8aMJddwqR5Fx70tjxo4lb4r'
access <- '1195948151179501569-THuTApWDbYUrbooDA0iSldWpgY63WT'
accessSecret <- 'OY5ESKILi1GgVivsbM1JeM3UmWLISO7ToADW8V9ZlZL4v'

setup_twitter_oauth(api, apiSecret, access, accessSecret)
```

# Data Import
```{r}
tweets <- searchTwitter("#rstats", 1000)
tweets_clean <- strip_retweets(tweets)
tweets_tbl <- twListToDF(tweets_clean) %>%
  transmute(text, 
            screenName, 
            favoriteCount, 
            retweetCount, 
            len_tweets = str_count(text))
```

# Analysis
```{r}
#calculate the relationship between length of tweet and other variables
corRetweet <- cor.test(tweets_tbl$len_tweets, tweets_tbl$retweetCount, method = "pearson")
corPop <- cor.test(tweets_tbl$len_tweets, tweets_tbl$favoriteCount, method = "pearson")
```
The correlation between length of tweet and retweet popularity was `r corRetweet$estimate` `r ifelse(corRetweet$p.value >= .05, "(p>=.05)", "(p<.05")`,  which is `r ifelse(corRetweet$p.value >= .05, "not", "")` statistically significant. 

The correlation between length of tweet and likes/favorites was `r corPop$estimate` `r ifelse(corPop$p.value >= .05, "(p>=.05)", "(p<.05")`,  which is `r ifelse(corPop$p.value >= .05, "not", "")` statistically significant. 

# Visualization
- visualize the relationship between length of tweet and retweet popularity
```{r}
ggplot(tweets_tbl, aes(len_tweets, retweetCount)) + 
  geom_point() + 
  labs(x = "length of tweet", y = "retweet popularity")
```

- visualize the relationship between length of tweet and likes/favorites
```{r}
ggplot(tweets_tbl, aes(len_tweets, favoriteCount)) + 
  geom_point() + 
  labs(x = "length of tweet", y = "likes/favorites")
```

